---
title: "Final Group Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up the data

```{r- setup}
library(fpp3)

credit <- read.csv("credit.csv")

creditIncr <- transform(credit, credit_in_millions = rev(credit_in_millions))
```

## Setting up tsibble

```{r- tsibble}
creditIncr %>% 
  mutate(Month = seq(as.Date("1981/1/1"), by = "month", length.out = nrow(creditIncr))) %>%
  mutate(Month = yearmonth(Month)) %>% 
  as_tsibble(index = Month) -> TSCredit

TSCredit %>% 
  autoplot()
```

## Differencing

```{r- differencing}
TSCredit %>%
  features(credit_in_millions, unitroot_kpss)

TSCredit %>%
  features(credit_in_millions, unitroot_ndiffs)

TSCredit_Diff <- TSCredit %>%
  mutate(y = credit_in_millions) %>% 
  mutate(y = difference(y, 12)) %>% 
  mutate(y = difference(y))

TSCredit_Diff %>% 
  autoplot(y)
```

## Creating train and test

```{r- train and test}
train <- TSCredit_Diff %>% 
  filter(Month < yearmonth("2021 Jan"))

test <- TSCredit_Diff %>% 
  filter(Month >= yearmonth("2021 Jan"))
```

## Models without stretch tsibble so they run faster to look for mistakes

```{r- models}
TSCredit_Diff %>% 
  model(lm = TSLM(credit_in_millions ~  trend() + season()),
        Drift= RW(credit_in_millions ~ drift()),
        hw = ETS(credit_in_millions),
        Mean = MEAN(credit_in_millions),
        SNaive = SNAIVE(credit_in_millions),
        NNETAR(sqrt(credit_in_millions))
        )
```

## Cross Validation (stretch tsibble)

```{r- stretch}
fit <- TSCredit_Diff %>% 
  stretch_tsibble(.init = 48, .step = 24) %>% 
  model(
    lm = TSLM(credit_in_millions ~  trend() + season()),
    Drift= RW(credit_in_millions ~ drift()),
    hw = ETS(credit_in_millions),
    SNaive = SNAIVE(credit_in_millions),
    NNETAR(sqrt(credit_in_millions))
  )

fit %>% 
  forecast(h= "12 months") %>% 
  accuracy(TSCredit_Diff) %>% 
  arrange(RMSE)
```

## Fitting best model

```{r- best model}
BestModelFit <- train %>% 
  model(
    
  )
```

## Forecasting 12 months in future

```{r- forecasting}

```

## IF we want to use RMSE function (this is the last part of HW 7 I thought it would make interpretations easier but we can definitely remove it)

```{r}
preds <- forecast(BestModelFit, holdout)
y_preds <- preds$.mean

rmse <- function(y_actual, y_pred) {
  sqrt(mean((y_actual - y_pred)^2))
}

rmse(holdout$credit_in_millions, y_preds)
```
