---
title: "Final Group Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setting up the data

```{r- setup}
library(fpp3)
library(ggeasy)
credit <- read.csv("credit.csv")
creditIncr <- transform(credit, credit_in_millions = rev(credit_in_millions))
```

## Setting up tsibble

```{r- tsibble}
creditIncr %>% 
  mutate(Month = seq(as.Date("1981/1/1"), by = "month", length.out = nrow(creditIncr))) %>%
  mutate(Month = yearmonth(Month)) %>% 
  as_tsibble(index = Month) -> TSCredit
TSCredit %>% 
  autoplot()
```

## Differencing

```{r- differencing}
TSCredit %>%
  features(credit_in_millions, unitroot_kpss)
TSCredit %>%
  features(credit_in_millions, unitroot_ndiffs)
TSCredit_Diff <- TSCredit %>%
  mutate(y = credit_in_millions) %>% 
  mutate(y = difference(y, 12)) %>% 
  mutate(y = difference(y))
TSCredit_Diff %>% 
  autoplot(y)
TSCredit_Diff %>% 
  gg_tsdisplay(y, plot_type='partial')
```

## Creating train and test

```{r- train and test}
train <- TSCredit_Diff %>% 
  filter(Month < yearmonth("2021 Jan"))
test <- TSCredit_Diff %>% 
  filter(Month >= yearmonth("2021 Jan"))
```

## Models without stretch tsibble so they run faster to look for mistakes

```{r- models}
TSCredit_Diff %>% 
  model(lm = TSLM(credit_in_millions ~  trend() + season()),
        Drift= RW(credit_in_millions ~ drift()),
        hw = ETS(credit_in_millions),
        Mean = MEAN(credit_in_millions),
        SNaive = SNAIVE(credit_in_millions),
        nnet = NNETAR(sqrt(credit_in_millions))
        )
```

## Cross Validation (stretch tsibble)

```{r- stretch}
fit <- TSCredit_Diff %>% 
  stretch_tsibble(.init = 48, .step = 24) %>% 
  model(ETS = ETS(credit_in_millions),
        SES = ETS(credit_in_millions~ error("A") + trend("N") + season("N")),
        Damped = ETS(credit_in_millions ~ error("A") + trend("Ad") + season("N")),
        stepwise = ARIMA(credit_in_millions)
  )


#Eliminated models::
#Drift= RW(credit_in_millions ~ drift()),
#nnet = NNETAR(sqrt(credit_in_millions))
#hw = ETS(credit_in_millions ~ error("M") + trend("Ad") + season("M"))
# additive = ETS(credit_in_millions ~ error("A") + trend("A") + season("A")),
#multiplicative = ETS(credit_in_millions ~ error("M") + trend("A") + season("M"))
#Holt = ETS(credit_in_millions ~ error("A") + trend("A") + season("N")),
#lm = TSLM(credit_in_millions ~  trend() + season()),
#SNaive = SNAIVE(credit_in_millions),
#K1 = TSLM(credit_in_millions ~ trend() + fourier(K = 1)), 
#K2 = TSLM(credit_in_millions ~ trend() + fourier(K = 2)),
#K3 = TSLM(credit_in_millions ~ trend() + fourier(K = 3)),
#K4 = TSLM(credit_in_millions ~ trend() + fourier(K = 4)),
#K5 = TSLM(credit_in_millions ~ trend() + fourier(K = 5)),
#K6 = TSLM(credit_in_millions ~ trend() + fourier(K = 6)))
#arima210 = ARIMA(credit_in_millions ~ pdq(2,1,0)),
#arima013 = ARIMA(credit_in_millions ~ pdq(0,1,3)),
#search = ARIMA(credit_in_millions, stepwise=FALSE)

 
fit %>% 
  forecast(h= "12 months") %>% 
  accuracy(TSCredit_Diff) %>% 
  arrange(RMSE)


#models i havent fit yet 

```

## Fitting best model

```{r- best model}
BestModelFit <- train %>% 
  model(
    stepwise = ARIMA(credit_in_millions, stepwise = FALSE, approximation = FALSE)
  )
BestModelFit %>% 
  forecast(h= "12 months") %>% 
  accuracy(TSCredit_Diff) %>% 
  arrange(RMSE)
```

## Forecasting 12 months in future

```{r- forecasting}
fit %>% 
  forecast(h= "12 months") %>% 
  accuracy(TSCredit_Diff) %>% 
  arrange(RMSE)
```

## IF we want to use RMSE function (this is the last part of HW 7 I thought it would make interpretations easier but we can definitely remove it)

```{r}
preds <- forecast(BestModelFit, test)
y_preds <- preds$.mean
rmse <- function(y_actual, y_pred) {
  sqrt(mean((y_actual - y_pred)^2))
}
rmse(test$credit_in_millions, y_preds)

#When using the stepwise model to predict credits for the Galactic Empire for the next 12 months, the typical miss we expect is about 0.09 credits. 
```

## Creating a new csv file

```{r}
write.csv(
  BestModelFit,
  file = "predictions.csv",
  row.names = FALSE
)
```

